\documentclass{article}

\usepackage{titlesec}
\usepackage[margin=1in]{geometry}
\usepackage{titling}
\pagenumbering{gobble}


\titleformat{\section}
{\huge\bfseries}
{$ $}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries\Large}
{$ $}
{0em}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{$ $}
{0em}
{}[---]


\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries
\theauthor}




\vspace{.25em}

kamal\_nwf@protonmail.com --- github.com/brokamal --- brokamalblog.vercel.app\\
Surabaya, Indonesia 

\end{center}

}



\begin{document}

\title{Curriculum Vitae}
\author{Mohammad Kamal}

\maketitle

\section{About me}
Bachelor student of Informatics Engineering in Institut Teknologi Sepuluh Nopemeber with main interests in Web Development,Computer Networking,Artificial Intellegence, and Creative Work. Experienced in web programming using Codeigniter, Basic computer networking, and graphic design. 
\\[1em]
Extremely passionate in learning things inside and outside of computer science field. Including but not limited to : Languages, History, Geography, and Creative endeavors. 
\section{Technical Skills}



\subsubsection{Programming}
C, C++, Python, Java, JavaScript
\subsubsection{Scripting}
Python, Bash, zsh
\subsubsection{Web Development Framework}
CodeIgniter, React.js, Next.js
\subsubsection{Markup}
HTML, Markdown, LaTeX
\subsubsection{Tools}
Terminal, tmux, Neovim, Programming IDE
\subsubsection{Database}
mySQL, PostgreSQL
\subsubsection{Design}
Blender, Inkscape, GIMP

\section{Education}
{\Large $ \bullet $ 2018-2021} \\
{Sekolah Menengah Atas Negeri Delapan, Bandung}
\\[2em]
{\Large $ \bullet $ 2021-2024} \\
{Institut Teknologi Sepuluh Nopember, Surabaya}
\\
{Bachelor Degree of Informatics Engineering}
\subsubsection{Relevant Coursework:}
Data Structure, Design and Analysis Algorithm, Database Management, Web Programming,Operating System, Computer Networking, Object Oriented Programming, Framework-based Programming. Artificial Intellegence. Computer Graphics, Knowledge Based System Engineering.

\section{General Skills}

\subsection{Languages}
Can speak: Indonesian, English, Sundanese \\
Can read: Spanish 

\subsection{Experiences}
\subsubsection{Lead Designer}
Responsible for leading a team of designer in designing Eight League media. Designed the logo and templates for Eight League.

\subsection{Project Experiences}
\subsubsection{ServerClientChat - GUI Application}
ServerClientChat is a GUI application that I created for my Object Oriented Programming course final project. It's a simple chat application 
that provide a chat communication between server and client. It also has translation API for any languages on google translate that translateto English. This application was written in Java.

\subsubsection{CuacaApp - Web Application}
CuacaApp is a web application that displays weather information. Cuaca App fetches data from an API that received it's data from BMKG. It only provides weather data from provinces of Indonesia. This web application was made using React.js  

\subsubsection{Pharmacy Management System - Web Application}
This web application was made for the final project of Framework-based Programming course. It's a web appliation inteded for managing the logistics and sales for a pharmacy. It has many features such as: Authentication, Dashboard, Costumer data, Staff data, Casheer dashboard, and logistic management dashboard. It uses database containing pharmaceutical information, including name, catergory, price, and stocks. This application was made using CodeIgniter and mySQL database.

\end{document}













